Proposal Draft

### 2020-07-18 proposal draft .Rmd
VIX data cleaning

add a comment

@@

```{r, message=FALSE}
library(formattable)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(tsibble)
library(tsibbledata)
library(feasts)
library(normtest)
library(moments)
library(ggthemes)
library(ggpubr)
library(knitr)
library(kableExtra)
```

@@

>>>>

@@

```{r, message=FALSE}
#library(formattable)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(tsibble)
library(tsibbledata)
library(feasts)
library(normtest)
library(moments)
library(ggthemes)
library(ggpubr)
library(knitr)
library(kableExtra)
```

@@

## VIX analysis

```{r,message=F}
# data cleaning and import 
vix <- read.csv("^VIX.csv")
vix <- vix %>% dplyr::select("Date","Adj.Close")

vix$logvix <- log(vix$Adj.Close)

# previous day log vix values
prev <- matrix(0,nrow = nrow(vix)+1,ncol = 1)
for (i in 1:nrow(vix)){
  prev[1,1] <- c("NA")
  prev[i+1,1] <- vix$logvix[i]
}
prev <- as.data.frame(prev)
prev <- prev[-c(1:178,6179),1]

require(zoo)
MA5 <- rollmean(vix$logvix,5,align = "center")
MA5 <- as.data.frame(MA5) # average of past week
MA5 <- MA5[-c(1:174),1] # including only 6000 obs

MA22 <- rollmean(vix$logvix,22,align = "center")
MA22 <- as.data.frame(MA22) # average of past month
MA22 <- MA22[-c(1:157),1] # including only 6000 obs

logvix <- vix[-c(1:178),c(1,3)] # delete the adjusted vix col, only keep 6000 obs
logvix <- cbind(logvix,prev,MA5,MA22)
# export the dataset to csv. including only trading days and log returns 
temp <- logvix[,2:5]
write_csv(temp,"vixlog.csv")
# the logvix, previous log vix and moving average values have the same length in the final file. 
```
